Word learning at the semantics pragmatics interface

### 2020-04-13 paper/supplementary_material.Rmd
begin fleshing out model math

@@

The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing the utterance. Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We assume that a listener's knowledge of a word's semantics is graded (not categorical). That is, for each object involved there is a probability $p$ that the literal listener knows the word for it. For each of the novel objects, this semantic knowledge is 0, which assumes that the novel word is equaliy likely to refer to the novel object as it is to refer to the familiar object. For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object (its expected acquisition trajectory) as well as on the child's age.

@@

\begin{equation} 
to be adjusted .... P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
\end{equation}

>>>>

$$
P_{L}(r \mid u)\propto P_{S}(u \mid r) \cdot P(r \mid \rho_i) \\ 
P_{S}(u \mid r)\propto Informativity(u;r)^{\alpha_i} \\
Informativity(u; r) = P(r|u) \propto P(r \mid \rho_i) \cdot \mathcal{L}(u \mid \theta_{ij})
$$

@@

The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance. Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the  listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel objects are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will pick out the familiar referent with probability $\theta + \frac{1 - \theta}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with  probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time. For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

@@

<!-- \begin{equation}  -->
$$P^{mixture}_{L_1}(r, \mathcal{L}|u) = \phi \cdot P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)$$
<!-- \end{equation}  -->
